---
title: 'Lecture 1: Spatial Data Viz'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(message = FALSE)
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(fig.width = 7.5)
knitr::opts_chunk$set(fig.height = 5.5)
knitr::opts_chunk$set(fig.align = 'center')
library(tidyverse)
library(leaflet)
```


## Spatial Data Viz Overview

Data visualization is an essential part of the statistical analysis process, both for exploratory analyses and summarizing findings.

##### Exploratory Data Analysis

- Used for data quality checks

- Help explore and understand the data

- Typically, not seen by anyone else

##### Polished Data Visualization

- Used to summarize data in presentations or papers

- Should *stand alone* with appropriate titles, axes, labels, and captions

- `ggplot2` makes creating polished figures easier: [cheat sheet](https://www.rstudio.com/wp-content/uploads/2016/11/ggplot2-cheatsheet-2.1.pdf)

## Spatial Data Viz Tools

There are many tools for creating spatial figures (GIS software, Tableau, etc...), but we will exclusively use R and the wide range of packages within it.

In particular, some options include:

- `ggplot2`

- `ggmap`

- `leaflet`

- `RgoogleMaps`

- `tmap`

- and many others...


## Point Data

### Point Data: What is this?
```{r, fig.align= 'center'}
set.seed(01082021)
uber <- read_csv('uber_coords.csv') %>% sample_n(200)

plot(y = uber$Lat, x=uber$Lon, xlab = 'Longitude', ylab = 'Latitude')
```


### Point Data: How about now?
```{r, fig.cap = 'Location of Uber pickups in the New York City area. The points represent a random sample of locations.', echo = T}
leaflet(uber) %>%
  addTiles() %>%
  addCircles(lng = ~Lon, lat = ~Lat)
```


## Active Learning Exercise: Seattle Police Calls Data Viz

Explore the Seattle police dataset (or a spatial dataset of your own) and leaflet to make an interactive data visualization.

```{r, message = T, echo = T}
seattle <- read_csv('SeattlePolice.csv')
```

The [leaflet overview](https://rstudio.github.io/leaflet/) is a great resource for getting started.
